Efficient pedigree recording for fast population genetics simulation

### 2018-01-26 forwards_paper.tex
author affils

\title{Efficient pedigree recording for fast population genetics simulation}
\author{Jerome Kelleher,
        Kevin R. Thornton,
        Jaime Ashander, and
        Peter L. Ralph}
\maketitle

>>>>

\title{Efficient pedigree recording for fast population genetics simulation}
\author{Jerome Kelleher\footnote{Big Data Institute, University of Oxford},
        Kevin R. Thornton\footnote{Ecology and Evolutionary Biology, University of California at Irvine},
        Jaime Ashander\footnote{Ecology and Evolutionary Biology, University of California at Los Angeles}, and
        Peter L. Ralph\footnote{Institute for Ecology and Evolution, University of Oregon}}
\maketitle
